### 2017-11-12 Maths Notes/D2/Travelling Salesman Problem/Travelling Salesman Problem.tex
Notes and Timetable update

\begin{document}
\begin{center}
\underline{\huge Allocation Problems}
\end{center}
\section{Cost Matrices}
\begin{itemize}
\item Require the same number of tasks as workers
\item Only relative costs are important
\end{itemize}
To find a reduced cost matrix:
\begin{enumerate}
\item Subtract the least value in each row from each element of that row
\item Using the new matrix, subtract the least value in each column from each element in that column
\end{enumerate}
\section{Hungarian algorithm}
\begin{enumerate}
\item Find the reduced cost matrix
\item Determine the minimum number of horizontal or vertical straight lines which will cover all the zeros in the matrix
\begin{itemize}
\item If lines $\geqslant$ n, where the matrix is n$\times$n then STOP
\item If lines $<$n, the matrix can be improved and continue 
\end{itemize}
\item Draw in the lines and look for the smallest uncovered element, call it $e$
\item Add $e$ to all covered elements, add it twice if covered twice
\item Subtract $e$ from \textbf{all} elements of the matrix (even those that just had $e$ added)
\item Repeat steps 2-5 until an optimal solution is found
\end{enumerate}
\subsection{Example}
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&250&80&160\\
\hline
Percival&230&90&150\\
\hline
Spike&230&110&140\\
\hline
\end{tabular}\\
\\
\textbf{Find the reduced cost matrix - First process rows}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&170&0&80\\
\hline
Percival&140&0&60\\
\hline
Spike&120&0&30\\
\hline
\end{tabular}\\
\\
\textbf{Find the reduced cost matrix - process columns}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&0&50\\
\hline
Percival&20&0&30\\
\hline
Spike&0&0&0\\
\hline
\end{tabular}\\
\textbf{Draw lines to cover zeros}\\
$
\begin{array}{|c|c|c|c|}
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartB}}&
\multicolumn{1}{c}{}\\
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&0&50\\
\hline
Percival&20&0&30\\
\hline
\tikzmark{StartA}Spike&0&0&\tikzmark{EndA}0\\
\hline

\multicolumn{1}{c}{}&
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndB}}}&
\multicolumn{1}{c}{}\\
\end{array}\\
$
\DrawLine[red, very thick,dotted]{StartA}{EndA}
\DrawVLine[red,very thick,dotted]{StartB}{EndB}
\\
\textbf{Compare to dimension of matrix}\\
2 Lines$\leqslant$3$\times$3 matrix\\
\\
\textbf{Find the smallest uncovered element}\\
20 (Percival digging)\\
\\
\\
\textbf{Add e to all covered elements, and add twice for double covering}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&50&20&50\\
\hline
Percival&20&20&30\\
\hline
Spike&20&40&20\\
\hline
\end{tabular}\\
\\
\textbf{Subtract e from all elements}\\
\begin{tabular}{|c|c|c|c|}
\hline
&Dig&Weed&Cut\\
\hline
Boris&30&0&30\\
\hline
Percival&0&0&10\\
\hline
Spike&0&20&0\\
\hline
\end{tabular}\\
\\
\textbf{Draw lines to cover zeros}\\
\\
$
\begin{array}{|c|c|c|c|}
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartA}}&
\multicolumn{1}{c}{\vspace{-.3cm}\tikzmark{StartB}}&
\multicolumn{1}{c}{}\\
\hline
&Dig&Weed&Cut\\
\hline
Boris&30&0&30\\
\hline
Percival&0&0&10\\
\hline
\tikzmark{StartC}Spike&0&20&\tikzmark{EndC}0\\
\hline
\multicolumn{1}{c}{}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndA}}}&
\multicolumn{1}{c}{\raisebox{.6\normalbaselineskip}{\tikzmark{EndB}}}&
\multicolumn{1}{c}{}\\
\end{array}\\
$
\DrawVLine[red, very thick,dotted]{StartA}{EndA}
\DrawVLine[red, very thick,dotted]{StartB}{EndB}
\DrawLine[red, very thick,dotted]{StartC}{EndC}
\\
\textbf{Compare to dimension of matrix}\\
3 lines=$3\times3$ matrix - Optimal solution
\section{Dummy Locations}
When the problem is not n$\times$n a dummy location is used, this has zeroes in all the elements.
\subsection{Example}
\begin{tabular}{|c|c|c|c|}
\hline
&Task A&Task B&Task C\\
\hline
Mark&12&23&15\\
\hline
Nicky&14&21&17\\
\hline
Nigel&13&22&20\\
\hline
Susie&14&24&13\\
\hline
\end{tabular}\\
\\
\textbf{Add another task with zero cost}\\
\begin{tabular}{|c|c|c|c|c|}
\hline
&Task A&Task B&Task C&Task D\\
\hline
Mark&12&23&15&0\\
\hline
Nicky&14&21&17&0\\
\hline
Nigel&13&22&20&0\\
\hline
Susie&14&24&13&0\\
\hline
\end{tabular}\\
\\
\textbf{This is then processed as usual}
\section{Incomplete data}
The algorithm can also work on incomplete data (where a person cannot to a task). To do this assign values to the tasks that cannot be done that are at least \textbf{twice as large} as the largest value.
\subsection{Example}
\begin{tabular}{|c|c|c|c|c|}
\hline
&Chinese&French&Indian&Italian\\
\hline
Denis&-&27&15&40\\
\hline
Hilary&14&21&17&13\\
\hline
Robert&20&-&13&-\\
\hline
Trudy&14&24&10&30\\
\hline
\end{tabular}
\newpage
\textbf{The cells with dashes in are then replaced with 100}\\
\begin{tabular}{|c|c|c|c|c|}
\hline
&Chinese&French&Indian&Italian\\
\hline
Denis&\textcolor{red}{100}&27&15&40\\
\hline
Hilary&14&21&17&13\\
\hline
Robert&20&\textcolor{red}{100}&13&\textcolor{red}{100}\\
\hline
Trudy&14&24&10&30\\
\hline
\end{tabular}\\
\\
\textbf{This can then be processed as normal}
\end{document}

>>>>

\begin{document}
\begin{center}
\underline{\huge Travelling Salesman Problem}
\end{center}
\section{Definitions}
The travelling salesman problem looks for a \textbf{walk} that gives the minimum \textbf{tour}.\\
\\
\textbf{Walk} - A finite series of edges so that the end of one vertex is the start of the next\\
\\
\textbf{Tour} - A walk that visits every vertex and returns to the starting vertex
\\
\textbf{Add more information about upper and lower bounds here when you understand it more}
\section{The differences between classical and practical problems}
\textbf{Classical Problem} - Must visit each vertex \textbf{only once} before returning to the start.\\
\textbf{Practical Problem} - Must visit each vertex \textbf{at least once} before returning to the start
\section{Converting a network into a complete network of least distances}
If a network is converted into a complete network of least distances, the classical and practical problem are the same.\\
\\
To create a complete network of least distances, you must ensure the \textbf{triangle inequality} holds for all triangles in the network.\\
\\
\textbf{Triangle inequality:}\\
The longest side of any triangle $\leqslant$ The sum of the two shorter sides\\
\\
In a network where the triangle inequality does not hold, replace the longest arc with the sum of the two shorter ones.
\end{document}
